Automated Essay Scoring

### 2018-05-10 paper/acl17-latex/paper.tex
finished abstract

\begin{document}
\maketitle
\begin{abstract}
  Recent advances in deep learning have produced state of art results in
  the task of automated essay scoring. The performance of these
  systems are not tested are approaching human level in the evaluation metrics,
  but their performance in actual scenarios is not explored. In this paper we explore
  how well these systems perform in real life scenarios as compared to non-neural
  models. We also explore some ways to overcome these shortcomings.
\end{abstract}

>>>>

\begin{document}
\maketitle
\begin{abstract}
  Automated essay scoring systems are used in evaluating and scoring student essays written based on a given prompt. Recent advances in Deep Learning and Natural Language Processing have produced state of art results in this task. The performance of these systems are approaching human level according to the evaluation metrics, but their qualitative performance in actual scenarios is not explored. In this paper we explore these systems perform in real life scenarios as compared to other non-neural models. We also explore some ways to overcome these shortcomings.
\end{abstract}
